### 2022-07-11 README.Rmd
README updated

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for regression analysis and hypothesis testing. The core computational routines are implemented with the 'Eigen' C++ library and 'RcppEigen' interface, with OpenMP for parallel computation. Details of the testing procedures are given in [Kim, MacEachern, and Peruggia (2021)](https://arxiv.org/abs/2112.09206).

>>>>

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for regression analysis and hypothesis testing. The core computational routines are implemented with the [Eigen](https://eigen.tuxfamily.org/index.php?title=Main_Page) C++ library and [RcppEigen](https://cran.r-project.org/web/packages/RcppEigen/index.html) interface, with OpenMP for parallel computation. Details of the testing procedures are given in [Kim, MacEachern, and Peruggia (2021)](https://arxiv.org/abs/2112.09206).
